---
title: "Iteration and List Columns"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
```

```{r}
knitr::opts_chunk$set(
        echo = TRUE,
        warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() +theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Here's some lists.

```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)

l

l$mat

l[["mat"]][1, 3]

l[[1]]
l[[4]]
```

```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```


Let's reuse the function we wrote last time.

```{r}
mean_and_sd = function(x) {
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
}
```


Let's use the function to take the mean and sd of all samples

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```


## Use a for loop

Create output list, and run a for loop

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}
```


## Do the same thing 

but with `map` instead

```{r}
output = map(list_norm, mean_and_sd)
```


Let's do a couple of other things

```{r}
output = 
  map(list_norm, mean_and_sd) |> 
  bind_rows()

output = map_dfr(list_norm, mean_and_sd)

output = map_dbl(list_norm, IQR)
```


## List columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )

listcol_df

listcol_df |> 
  filter(name %in% c("a", "b"))

listcol_df |> 
  select(-samp)
```

```{r}
listcol_df[["samp"]][["a"]]
```


Compute mean and sd

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

map(listcol_df[["samp"]], mean_and_sd)
```

Add a list column

```{r}
listcol_df |> 
  mutate(output = map(samp, mean_and_sd),
  iqr = map(samp, IQR))

listcol_df |> 
  mutate(
    output = map(samp, mean_and_sd),
    iqr = map_dbl(samp, IQR)) |> 
  select(-samp) |> 
  unnest(output)
```


### NSDUH 

This is a version of our function from last time.

```{r}
nsduh_table_format = function(html, table_num) {
  
  out_table = 
    nsduh_html |> 
    html_table() |> 
    nth(table_num) |> 
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(out_table)
  
}
```

We need to import the html, and then extract the correct tables.

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```

```{r}
nsduh_table_format(html = nsduh_html, table_num = 1)
nsduh_table_format(html = nsduh_html, table_num = 4)
nsduh_table_format(html = nsduh_html, table_num = 5)
```

```{r}
nsduh_df = 
  tibble(
    drug = c("marj", "cocaine", "heroin"),
    table_n = c(1, 4, 5)
  ) |> 
  mutate(table = map(table_n, nsduh_table_format, html = nsduh_html)) |> 
  unnest(table)

nsduh_df |> 
  filter(State == "New York")
```

